Practical Optional Types for Clojure

### 2015-02-06 icfp15-typedclojure.tex
fix fieldexp formatting
update T-GetHMap proof

\begin{lstlisting}
(defn grandparent [^File f]
  (when f
    (let [f (. f (getParent))]
      (when f
        (. (new File f) (getParent))))))
\end{lstlisting}
%(some-> f (.getParent) (File.) (.getParent))

@@

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(defmulti tree-str (fn [e :- Expr] (:op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}

>>>>

\begin{lstlisting}
(defn grandparent [^File f]
  (when f
    (let [f (. f (getParent))]
      (assert f "Expected parent string, got nil")
      (. (new File f) (getParent)))))
\end{lstlisting}
%(some-> f (.getParent) (File.) (.getParent))

@@

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(defmulti tree-str (fn [e :- Expr] (get :op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}
